Experiments on ANTS Algorithms Without Communication

### 2014-12-09 paper/draft.tex
added stuff to intro

We study the \emph{Ants Nearby Treasure Search} (ANTS) problem for modelling collective foraging in animal groups. $k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location.

\subsection{Related Works}

>>>>

We study the \emph{Ants Nearby Treasure Search} (ANTS) problem for modelling collective foraging in animal groups. $k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location. The problem is a generalization of a previously studied problem, the \emph{cow-path} problem, which is the case where $k = 1$.

Our project is a combination of a reading project and an experimental project. For the reading project component, we survey three algorithms, two of which are by Feinerman et al., and the other by by Lenzen et al. The two algorithms by Feinerman et al. are the \emph{spiral} algorithm and the \emph{harmonic} algorithm. We name the algorithm by Lenzen et al. the \emph{lines} algorithm. For these algorithms, we consider case of uniformity, where all agents know the value of either $D$ or $k$, and the case of non-uniformity, where a value is unknown.
